A linearization procedure for constrained multibody systems

### 2013-02-17 PetersonGedeHubbard2012.tex
Added subscript to identity matrix in definition of C_2
Changed speeds to states in sentence discussing constraint Jacobians.

\begin{align}
  \label{eq:C_0}
  C_0 &\triangleq \left[ I_{n \times n} - P_{qd}(\nabla_{\bm{q}}
    \bm{f}_{c} P_{qd})^{-1} \nabla_{\bm{q}} \bm{f}_{c} \right] P_{qi}\\
  \label{eq:C_1}
  C_1 &\triangleq -P_{ud}(\nabla_{\bm{u}} \bm{f}_{v} P_{ud})^{-1}
  \nabla_{\bm{q}} \bm{f}_{v} \\
  \label{eq:C_2}
  C_2 &\triangleq \left[I - P_{ud} (\nabla_{\bm{u}}\bm{f}_{v} P_{ud})^{-1} \nabla_{\bm{u}}
    \bm{f}_{v} \right] P_{ui}\\
  \label{eq:Pq}
  \bm{q} &= P_{qi} \bm{q}_{i} + P_{qd} \bm{q}_{d} \\
  \label{eq:Pu}
  \bm{u} &= P_{ui} \bm{u}_{i} + P_{ud} \bm{u}_{d}
\end{align}

@@

The choice of which state variables are taken to be independent may determine
whether $\nabla_{\bm{q}}\bm{f}_{c} P_{qd}$ and $\nabla_{\bm{u}} \bm{f}_{v}
P_{ud}$ are nonsingular.  These matrices depend upon the configuration $\bm{q}$
and constant parameters; for certain configurations or parameters, it may be
that the choice of independent state variables cannot be arbitrary.  While some
systems may permit a choice of independent state variables which are valid for
all configurations of interest, others may not.  Methods for automatically
selecting the ``best'' choice of independent state variables are discussed in
\cite{Reckdahl1996}; they involve computing the SVD of the Jacobian of the
constraint matrices to determine a set of independent speeds which will ensure
the non-singularity of the aforementioned matrices.

>>>>

\begin{align}
  \label{eq:C_0}
  C_0 &\triangleq \left[ I_{n \times n} - P_{qd}(\nabla_{\bm{q}}
    \bm{f}_{c} P_{qd})^{-1} \nabla_{\bm{q}} \bm{f}_{c} \right] P_{qi}\\
  \label{eq:C_1}
  C_1 &\triangleq -P_{ud}(\nabla_{\bm{u}} \bm{f}_{v} P_{ud})^{-1}
  \nabla_{\bm{q}} \bm{f}_{v} \\
  \label{eq:C_2}
  C_2 &\triangleq \left[I_{o \times o} - P_{ud} (\nabla_{\bm{u}}\bm{f}_{v} P_{ud})^{-1} \nabla_{\bm{u}}
    \bm{f}_{v} \right] P_{ui}\\
  \label{eq:Pq}
  \bm{q} &= P_{qi} \bm{q}_{i} + P_{qd} \bm{q}_{d} \\
  \label{eq:Pu}
  \bm{u} &= P_{ui} \bm{u}_{i} + P_{ud} \bm{u}_{d}
\end{align}

@@

The choice of which state variables are taken to be independent may determine
whether $\nabla_{\bm{q}}\bm{f}_{c} P_{qd}$ and $\nabla_{\bm{u}} \bm{f}_{v}
P_{ud}$ are nonsingular.  These matrices depend upon the configuration $\bm{q}$
and constant parameters; for certain configurations or parameters, it may be
that the choice of independent state variables cannot be arbitrary.  While some
systems may permit a choice of independent state variables which are valid for
all configurations of interest, others may not.  Methods for automatically
selecting the ``best'' choice of independent state variables are discussed in
\cite{Reckdahl1996}; they involve computing the SVD of the Jacobian of the
constraint matrices to determine a set of independent states which will ensure
the non-singularity of the aforementioned matrices.
